\documentclass{beamer}
\usetheme{Frankfurt} % Similar to the default 
\setbeamertemplate{footline}[page number]
\setbeamercovered{invisible}
\setbeamertemplate{navigation symbols}{ }

\usepackage{graphicx}
\usepackage{lmodern} %this font kills an annoying compliation warning, and is almost the same as the default.
\usepackage{subfigure} %for side to side figures
\usepackage{hyperref} %to create internal links

%title 'n stuff
\title{Migration and Growth}
\author{David Jinkins}
\institute
{
    Pennsylvania State University\\
    \medskip
    {\emph{david.jinkins@gmail.com}}
}
\date{\today}

\begin{document}
\begin{frame}
    \maketitle
\end{frame}

\section{Introduction}
\begin{frame}
    \frametitle{Gains from migration are big}
    \begin{itemize}
        \item Gains from trade are small: Arkolakis et al (AER 2012)
        \item Gains from tariff reduction are small: Alvarez Lucas (JME 2006)
        \item Static gains from labor migration are huge: Clemens (JEP 2011)
        \item Dynamic gains from labor migration: this project.
    \end {itemize}
\end{frame}

\begin{frame}
    \frametitle{Why do economies grow?}
    \begin{itemize}
        \item Chicago's ideas vs. blueprints debate.
        \item Blueprints, patents, quality ladders: Grossman Helpman (1991), Kortum (1997)
        \item In person je ne sais quoi: Lucas (2009), Lucas Moll (2012)
        \item Why are Indian firms unproductive: Bad management/inventory: Bloom and Van Reenen (2010)
    \end {itemize}
\end{frame}

\begin{frame}
    \frametitle{Is migration good for non-migrants?}
        \begin{itemize}
            \item Clearly good for migrants--it's a choice!
            \item Brain drain/Brain gain (ton of literature)
            \item Remittances (also ton of literature)
            \item This paper--moving technology back home
        \end{itemize}
\end{frame}

\section{Model}
\begin{frame}
    \frametitle{Preliminaries}
    \begin{itemize}
        \item Continuous time.
        \item Two Countries: Rich and Poor.
        \item Unit mass populations.
        \item Described by production cost distributions.
        \item One good, prod: $z^{-\theta}$.
        \item Utility is discounted production stream.
    \end{itemize}
\end{frame}


\end{document}
